---
title: "SCRIPT 1 -- DATA PROCESSING PT 1: Make ema dfs (sjdm task data only)"
date: "07.08.2026"
format:
  html:
    code-fold: true
    embed-resources: true
    toc: true
    toc-depth: 3
    df-print: paged
execute:
  echo: true
  warning: false
  message: false
---

set dir
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
```

display
```{css, echo=FALSE}
pre { max-width: 100%; overflow-x: auto; }
```


### source scripts with functions 
```{r, message=FALSE, warning=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("Functions/packages.R")
source("Functions/make_ema_sjdm_dfs.R")


```

### load packages 
```{r, message=FALSE, warning=FALSE}
loadpackages()
conflicts_prefer(dplyr::lag)
conflicts_prefer(data.table::first)
conflicts_prefer(rstatix::filter)
conflicts_prefer(dplyr::rename)
conflicts_prefer(dplyr::summarise)
conflicts_prefer(dplyr::summarize)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::arrange)
conflicts_prefer(dplyr::count)
conflicts_prefer(dplyr::filter)

```



## Load sjdm ema data
```{r}
# Set location of data (whenever there is a new data pull from pavlovia will have to update the date of the folder to match)
  # This data is just direct copy of "data" folder from ema task pavlovia proj
#data_folder_sjdm <- "sjdm_raw-data_5.19"
#data_folder_sjdm <- "sjdm_raw-data_5.27"
#data_folder_sjdm <- "sjdm_raw-data_6.24"
#data_folder_sjdm <- "sjdm_raw-data_7.08"



data_folder_sjdm <- "sjdm_raw-data_07.08"


all_files_sjdm <- list.files(data_folder_sjdm, pattern = "\\.csv$", full.names = TRUE)


# N files total
cat("total N of CSV files:\n")
print(length(all_files_sjdm))

#getwd()
```

## Clean old task versions
```{r}
# table with one row per file and for each fiel the ptid, n_cols, and colnames 

ema_sjdm_pt_csv_structure_table <- map_dfr(all_files_sjdm, function(f) {
  tmp <- read_csv(f, n_max = 1, show_col_types = FALSE) # read first row of each file to get col names and what data type each col is 
  tibble(
    file = basename(f), #ths just removes name of the folder from the path 
    pt_id = str_extract(basename(f), "(?<=EMA_)[^_]+"), # Pull out pt id from filename
    n_cols = ncol(tmp), # list how many cols the file has
    # paste all the column names into one string, separated by commas
    col_names = paste(names(tmp), collapse = ", ") # for each file, make a col that has all the colnames in the file listed in a string 
  )
})

#print(ema_sjdm_pt_csv_structure_table)


# identify all the unique csvs structures and which pts have their csvs structured like what 
ema_sjdm_unique_csv_structures <- ema_sjdm_pt_csv_structure_table %>%
  group_by(n_cols, col_names) %>%
  summarise(
    n_files = n(),
    pt_ids = paste(sort(unique(pt_id)), collapse = ", "),
    n_pts = length(unique(pt_id)),
    .groups = "drop"
  ) %>%
  arrange(desc(n_files)) %>%
  mutate(structure_label = paste0("s", row_number(), "_", n_cols, "col")) #name each structure type by num cols.

# ema_sjdm_unique_csv_structures %>% gt() %>% 
#   tab_header(title = "all the unique csvs structures in ema sjdm raw data files",
#              subtitle = "num files per each structure type and which pts have their csvs structured like what")
#list(ema_sjdm_unique_csv_structures$col_names)
#list(ema_sjdm_unique_csv_structures$n_files)
#list(unique(ema_sjdm_unique_csv_structures$pt_ids))

# tag each file with strucyre label # THIS IS WHAT WILL USE FOR ACTUALLY CLEANING AND READING IN THE DFS
files_with_structure <- ema_sjdm_pt_csv_structure_table %>%
  left_join(
    ema_sjdm_unique_csv_structures %>% select(n_cols, col_names, structure_label),
    by = c("n_cols", "col_names")
  ) %>%
  mutate(file_date = as.Date(str_extract(file, "\\d{4}-\\d{2}-\\d{2}")))
#files_with_structure
#files_with_structure %>% count(structure_label)


# table that arranges the cols in each structure side by side 
data_structures <- ema_sjdm_unique_csv_structures %>%
  mutate(col_name = strsplit(col_names, ", ")) %>%
  select(structure_label, col_name) %>%
  unnest(col_name) %>%
  group_by(structure_label) %>%
  mutate(colnumber = row_number()) %>%
  ungroup() %>%
  pivot_wider(names_from = structure_label, values_from = col_name)

#print(data_structures)
# data_structures %>% gt() %>%
#   sub_missing(missing_text = "") %>%
#   tab_header(
#     title = "the colnames within each of the 9 CSV data structure types",
#     subtitle = "colnames within each of the data structure types r listed vertically "
#   )

# For each file structure type, randomly look at 2 (can change to look through more like 10 which is better to get comprehensive look but keeping 2 for now since this is the max amt of files and  rows for each file structure that will print without having to scroll) 
set.seed(1)
sampled_peek <- files_with_structure %>%
  group_by(structure_label) %>%
  slice_sample(n = 2) %>%
  ungroup() %>%
  mutate(full_path = file.path(data_folder_sjdm, file)) %>%
  mutate(file_data = map(full_path, ~ read_csv(.x, n_max = 3, show_col_types = FALSE) %>%
                           mutate(across(everything(), as.character)))) %>%
  select(structure_label, pt_id, file, file_data) %>%
  unnest(file_data) %>%
  arrange(structure_label, pt_id, file)

#print(sampled_peek)
# sampled_peek %>% gt() %>%
#   tab_header(
#     title = "each of the 9 CSV data structure types list 3 rows from 2 random files",
#     subtitle = "to look through to get an idea of what each file looks like"
#   )

# Cleaner summary table for each file structure type (based on what i see )
ema_sjdm_structure_summary <- files_with_structure %>%
  group_by(structure_label, n_cols) %>%
  summarise(
    n_files = n(),
    first_file_date = min(file_date),
    last_file_date = max(file_date),
    .groups = "drop"
  ) %>%
  arrange(desc(n_files))

# ema_sjdm_structure_summary %>% gt() %>%
#   tab_header(
#     title = "list of 9 filetypes with dates")

# structure_descriptions col describes what each data structure is based off what data and cols is in each (ref dfs sampled_peek and data_structures) and which pts took each structure type (ref df ema_sjdm_unique_csv_structures) and date (if after study launch ema_sjdm_structure_summary)

structure_descriptions <- tibble(
  structure_label = c("s1_33col", "s2_6col", "s3_32col", "s4_32col",
                      "s5_23col", "s6_31col", "s7_23col", "s8_31col", "s9_31col"),
  
 description = c(
    #s1_33col 
    "real pt data (first file was from 2026-02-05 (when study launched) and latest from 2026-05-19). idnetifier is PUNS_ID, usses html-keyboard-response, has all new session tracking cols that i added in most recent index file version (session_number, session_phase, ema_start_date, ema_post_start_date))",
    
    #s2_6col 
    "aborted ema sessions (first file from 2026-02-09 and lates from 2026-05-19). pt opened link but didnt complete task",
    
    #s3_32col 
    "pre study-launch testing (first file from 2025-11-11 latest file from 2026-01-27) taken by 11 testers (puns team + fabla dev team) (9000, 9001, 9002, 9003, 9005, 9006, 9008, 9009, 9010, 9998, 9999)",
    
    #s4_32col 
    "pre study-launch testing (first file from 2025-09-24 latest file from 2025-11-11) older version of task while i was still building out so used html-button-response, taken by me with ids that I thought I could use for testing (1001-1012, 1013)  (beofre i realized i had to use ids that start with 9000 since real pts would start with 1000) and 4 fabla dev testing ids (9000, 9005, 9006, 9008)",
    
    #s5_23col 
    "pre study-launch testing (only instances from 2025-09-22) taken by me only once (R_ qualtrics id)",
    
    #s6_31col 
    "testing that i did post launch to test if the fabla webform was working (only instances from 2026-02-05) taken by 1 fabla dev tester (9005) and me (TESTAP999)",
    
    #s7_23col
    "pre study-launch testing (only instances from 2025-09-22) again outdated form of task so variables were old taken by me only once (R_ qualtrics id)",
    
    #s8_31col 
    "pre study-launch testing (only instance from 2025-11-10) taken by me only once using fabla dev testing id: 9005",
    

    #s9_31col 
    "pre study launch testing (only instances from 2025-09-24) taken by me only once (was using R_ qualtircs id bc hadnt configured PUNS_ID yet)"
  )
)

ema_sjdm_structure_summary <- ema_sjdm_structure_summary %>%
  left_join(structure_descriptions, by = "structure_label")

ema_sjdm_structure_summary %>% gt() %>%
  tab_header(
    title = "list of 9 filetypes with with descriptions of why each is different")
```

summarize structure of csvs from diff task types
```{r}
ema_sjdm_structure_summary_final <- ema_sjdm_structure_summary %>%
  select(structure_label, n_files, description) %>%
  mutate(
    full_structure_label = c(
      "real_study_data_finalized_task", #s1_33col
      "aborted_ema_session_no_trials", #s2_6col
      "prestudylaunch_v1", #s3_32col
      "prestudylaunch_v2", #s4_32col
      "prestudylaunch_v3", #s5_23col
      "postlaunch_testing", #s6_31col
      "prestudylaunch_v4", #s7_23col
      "prestudylaunch_v5", #s8_31col
      "prestudylaunch_v6" #s9_31col
    )
  ) %>%
  select(structure_label, full_structure_label, n_files, description)

# ema_sjdm_structure_summary_final %>%
#   gt() %>%
#   tab_options(table.width = pct(80)) %>%
#   tab_header(
#     title = "EMA SJDM CSV File Structures: Type and Description"
#   )
```




## Cleaning part 1 (clean old task versions + test pts + technical issues) 
```{r}
# Cleaningin + tibble checks 
files_clean_pts <- files_with_structure %>%
  left_join(
    ema_sjdm_structure_summary_final %>% select(structure_label, full_structure_label),
    by = "structure_label"
  )
files_clean_pts
#-----------------------------------------------------------------------------#
# B4 any cleaning
tibble(
  step = "b4 any cleaning",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_test_ids()
# after remove_test_ids
tibble(
  step = "after remove_test_ids",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_R_ids()
# after remove_R_ids
tibble(
  step = "after remove_R_ids",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_fabla_dev_testers()
# after remove_fabla_dev_testers
tibble(
  step = "after remove_fabla_dev_testers",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_amira_postlaunch_tests()
# after remove_amira_postlaunch_tests
tibble(
  step = "after remove_amira_postlaunch_tests",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_pts_with_severe_task_issues()
# after remove_pts_with_severe_task_issues
tibble(
  step = "after remove_pts_with_severe_task_issues",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))

#-----------------------------------------------------------------------------#
files_clean_pts <- files_clean_pts %>% remove_pts_with_severe_task_issues()
# after clean_pts_still_in_pre_trip
tibble(
  step = "after remove_pts_with_severe_task_issues",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))

```

## Cleaning part 2 (clean old files that should not be in dataset) 
```{r}
# Seems like even after last cleaning step there are 2 files using this data dtructure... take closer look 
files_clean_pts %>%
  filter(full_structure_label == "prelaunch_dev_test_button") %>%
  select(pt_id, file, file_date, structure_label, full_structure_label) %>% gt()

# ... okay these files are from pt_id 1013... file date is from october which is way before study launch... so seems like i also used 1013 to test accidently 

# Clean out these exact files (accidently tested under ID of an actual pt well b4 study launch)
  # for pt 1013 2-SRET-PUNS-EMA_1013_SESSION_2025-10-08_18h19.29.858.csv and 2-SRET-PUNS-EMA_1013_SESSION_2025-10-14_18h55.45.451.csv
files_clean_pts <- files_clean_pts %>% remove_old_files()
# after remove_old_files
tibble(
  step = "after remove_old_files",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
#-----------------------------------------------------------------------------#
# Clea 1015's files from before they enrolled (had to push back trip date)
files_clean_pts <- files_clean_pts %>% remove_1015_prereenrollment()
# after remove_1015_prereenrollment
tibble(
  step = "after remove_1015_prereenrollment",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))

#-----------------------------------------------------------------------------#
# Clean 1086's files from before they enrolled (had to push back trip date)
files_clean_pts <- files_clean_pts %>% remove_1086_may11_files()
# after remove_1086_may11_files
tibble(
  step = "after remove_1086_may11_files",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))


#-----------------------------------------------------------------------------#
# Clean 1027's files from before they enrolled (had to push back trip date)
files_clean_pts <- files_clean_pts %>% remove_1027_march22_files()
# after remove_1027_march22_files
tibble(
  step = "after remove_1027_march22_files",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))

```



## Cleaning part 3 (clean aborted EMA sessions) 
```{r}
files_clean_pts <- files_clean_pts %>% remove_aborted_sessions()
# after remove_aborted_sessions
tibble(
  step = "after remove_aborted_sessions",
  n_files = nrow(files_clean_pts),
  n_pts = length(unique(files_clean_pts$pt_id)),
  pt_ids = paste(sort(unique(files_clean_pts$pt_id)), collapse = ", "),
 structure_types_and_counts = files_clean_pts %>%
  count(full_structure_label, sort = TRUE) %>%
  mutate(line = paste0(full_structure_label, ": ", n)) %>%
  pull(line) %>%
  paste(collapse = "<br>")
) %>% gt()  %>%
  fmt_markdown(columns = structure_types_and_counts)  %>%
  tab_options(table.width = pct(80))
```


## Combine valid files 
```{r}
ema_sjdm_all <- map_dfr(files_clean_pts$file, function(f) {
  full_path <- file.path(data_folder_sjdm, f)
  read_csv(full_path, show_col_types = FALSE) %>%
    mutate(
      source_file = f,
      file_date = as.Date(str_extract(f, "\\d{4}-\\d{2}-\\d{2}"))
    )
})

tibble(
  step = "combined all valid files",
  n_rows = nrow(ema_sjdm_all),
  n_pts = length(unique(ema_sjdm_all$PUNS_ID)),
  pt_ids = paste(sort(unique(as.character(ema_sjdm_all$PUNS_ID))), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))
```
### Fix start dates
```{r}
# CHECK does any pt carry more than one ema start date 
ema_sjdm_all %>%
  distinct(PUNS_ID, ema_start_date, ema_post_start_date) %>%
  count(PUNS_ID) %>%
  filter(n > 1) %>%
  gt() %>%
  tab_header(title = "pts with >1 distinct start-date pair (pts who changed ema date in fabla. need to make consistent)")


# use latest start date (since most trip dates were pushed back)
ema_sjdm_all <- ema_sjdm_all %>%
  group_by(PUNS_ID) %>%
  mutate(
    ema_start_date = max(ema_start_date, na.rm = TRUE),
    ema_post_start_date = max(ema_post_start_date, na.rm = TRUE)
  ) %>%
  ungroup()

# should be empty 
ema_sjdm_all %>%
  distinct(PUNS_ID, ema_start_date, ema_post_start_date) %>%
  count(PUNS_ID) %>%
  filter(n > 1)
```


# Cleaning part 4 (remove trials without data + cleaning needed for data)
```{r}
#str(ema_sjdm_all)
#unique(ema_sjdm_all$trial_type)
#unique(ema_sjdm_all$which_experiment_phase)
tibble(
  step = "before keep_only_pairing_trials",
  n_rows = nrow(ema_sjdm_all),
  n_pts = length(unique(ema_sjdm_all$PUNS_ID))
) %>% gt() %>% tab_options(table.width = pct(80))

ema_sjdm_all %>%
  count(trial_type, which_experiment_phase) %>%
  arrange(desc(n)) %>% gt()

# filter to just pairings trials 
ema_sjdm_all <- ema_sjdm_all %>% keep_only_pairing_trials()


tibble(
  step = "after keeping only pairing choice trials",
  n_rows = nrow(ema_sjdm_all),
  n_pts = length(unique(ema_sjdm_all$PUNS_ID)),
  n_sessions = nrow(ema_sjdm_all) / 24
) %>% gt() %>% tab_options(table.width = pct(80))

# count pairing trials per session (one row per pt × session)
trials_per_session <- ema_sjdm_all %>%
  group_by(PUNS_ID, session_number, session_phase) %>%
  summarise(
    n_trials = n(),
    .groups = "drop"
  ) %>%
  arrange(PUNS_ID, session_number)



```
# Clean duplicate files 
```{r}

# remove duplicate files 
ema_sjdm_all <- ema_sjdm_all %>%
  mutate(session_phase_and_num = paste(session_phase, session_number, sep = "_"))


ema_sjdm_all <- ema_sjdm_all %>%
  group_by(PUNS_ID, session_phase_and_num) %>%
  mutate(
    n_files_per_session = n_distinct(source_file),
    n_trials_per_session = n(),
    is_duplicate_session = n_files_per_session > 1
  ) %>%
  ungroup()


ema_sjdm_all <- ema_sjdm_all %>%
  group_by(PUNS_ID, session_phase_and_num, source_file) %>%
  mutate(n_trials_per_file = n()) %>%
  ungroup()


df_duplicates <- ema_sjdm_all %>%
  filter(is_duplicate_session == TRUE)

tibble(
  step = "before duplicate removal",
  n_rows = nrow(ema_sjdm_all),
  n_unique_sessions = n_distinct(
    ema_sjdm_all$PUNS_ID,
    ema_sjdm_all$session_phase_and_num
  ),
  n_duplicate_sessions = ema_sjdm_all %>%
    filter(is_duplicate_session) %>%
    distinct(PUNS_ID, session_phase_and_num) %>%
    nrow(),
  n_pts = n_distinct(ema_sjdm_all$PUNS_ID)
) %>%
  gt() %>%
  tab_options(table.width = pct(80))

ema_sjdm_all <- ema_sjdm_all %>%
  arrange(PUNS_ID, session_phase_and_num, experiment_start) %>%
  group_by(PUNS_ID, session_phase_and_num) %>%
  filter(source_file == first(source_file)) %>%
  ungroup()


# recalculate AFTER removal
ema_sjdm_all <- ema_sjdm_all %>%
  group_by(PUNS_ID, session_phase_and_num) %>%
  mutate(
    n_files_per_session = n_distinct(source_file),
    n_trials_per_session = n(),
    is_duplicate_session = n_files_per_session > 1
  ) %>%
  ungroup()

# after table
tibble(
  step = "after duplicate removal",
  n_rows = nrow(ema_sjdm_all),
  n_unique_sessions = n_distinct(
    ema_sjdm_all$PUNS_ID,
    ema_sjdm_all$session_phase_and_num
  ),
  n_duplicate_sessions = ema_sjdm_all %>%
    filter(is_duplicate_session) %>%
    distinct(PUNS_ID, session_phase_and_num) %>%
    nrow(),
  n_pts = n_distinct(ema_sjdm_all$PUNS_ID)
) %>%
  gt() %>%
  tab_options(table.width = pct(80))
```


# Cleaning Part 5 remove pts still in progress (still taking pre trip EMAs) 
```{r}
ema_sjdm_all <- clean_pts_still_in_pre_trip(ema_sjdm_all)
tibble(
  step = "removed pts still in pre-trip EMAs",
  n_rows = nrow(ema_sjdm_all),
  n_pts = n_distinct(ema_sjdm_all$PUNS_ID),
  pt_ids = paste(sort(unique(as.character(ema_sjdm_all$PUNS_ID))), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))
```


## check TASK compliance
```{r}
ema_sjdm_all %>%
  group_by(PUNS_ID) %>%
  summarise(
    n_sessions = n_distinct(session_phase_and_num),
    .groups = "drop"
  ) %>%
  mutate(compliance_pct = round((n_sessions / 60) * 100, 1)) %>%
  gt() %>%
  tab_header(title = "TASK ONLY pre and post trip ema compliance") %>%
  tab_options(table.width = pct(80))

ema_sjdm_all %>%
  group_by(PUNS_ID, session_phase, session_day) %>%
  summarise(n_sessions = n_distinct(session_number), .groups = "drop") %>%
  mutate(phase_day = factor(
    paste0(session_phase, "_day_", session_day),
    levels = c(paste0("pre_day_", 1:10), paste0("post_day_", 1:10))
  )) %>%
  select(PUNS_ID, phase_day, n_sessions) %>%
  complete(PUNS_ID, phase_day, fill = list(n_sessions = 0L)) %>%
  pivot_wider(
    names_from  = phase_day,
    values_from = n_sessions,
    values_fill  = 0L
  ) %>%
  select(PUNS_ID, paste0("pre_day_", 1:10), paste0("post_day_", 1:10)) %>%
  gt() %>%
  tab_header(title = "TASK ONLY sessions per day per participant") %>%
  tab_options(table.width = pct(80))

ema_sjdm_all %>%
  filter(session_phase == "pre") %>%
  group_by(PUNS_ID) %>%
  summarise(
    n_sessions = n_distinct(session_number),
    .groups = "drop"
  ) %>%
  mutate(compliance_pct = round((n_sessions / 30) * 100, 1)) %>%
  arrange(desc(compliance_pct)) %>%
  gt() %>%
  tab_header(title = "TASK ONLY pre trip compliance") %>%
  tab_options(table.width = pct(80))
```


## Cleaning part 6 remove pts with rly low compliance 
```{r}
# remove pts with rly low compliance 
ema_sjdm_all <- remove_low_compliance_pts(ema_sjdm_all)
tibble(
  step = "removed rly low compliance pts",
  n_rows = nrow(ema_sjdm_all),
  n_pts = n_distinct(ema_sjdm_all$PUNS_ID),
  pt_ids = paste(sort(unique(as.character(ema_sjdm_all$PUNS_ID))), collapse = ", ")
) %>% gt() %>% tab_options(table.width = pct(80))
```




### Export 
```{r}
if (!dir.exists("pre-processed_ema-sjdm_data")) dir.create("pre-processed_ema-sjdm_data")
write_csv(ema_sjdm_all, "pre-processed_ema-sjdm_data/ema_sjdm_cleaned.csv")

```

