---
title: "SCRIPT 3 - EMPERICAL DATA ANALYSIS: Pre-Trip SS plots (all trials)"
date: "07.08.2026"
format:
  html:
    code-fold: true
    embed-resources: true
    toc: true
    toc-depth: 3
    df-print: paged
execute:
  echo: true
  warning: false
  message: false
---

set dire
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())

```

display
```{css, echo=FALSE}
pre { max-width: 100%; overflow-x: auto; }
```

hssm venv
```{r}
library(reticulate)
# use_python("/opt/anaconda3/envs/hssm_venv/bin/python")
use_condaenv("hssm_venv", required = TRUE)
```

py packages 
```{python}
import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from scipy.special import expit
from sklearn.linear_model import LogisticRegression
from scipy.interpolate import UnivariateSpline

```


### source scripts with functions 
```{r, message=FALSE, warning=FALSE}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("Functions/packages.R")

#source("Functions/puns-analyses_functions.R")
```

### load packages 
```{r, message=FALSE, warning=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
loadpackages()
conflicts_prefer(rstatix::filter)
conflicts_prefer(dplyr::rename)
conflicts_prefer(dplyr::summarise)
conflicts_prefer(dplyr::summarize)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::arrange)
conflicts_prefer(dplyr::count)
conflicts_prefer(dplyr::filter)

```

### load data
```{r}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
#setwd("..")

emas_pre <- read_csv("pre-processed_full-ema_data/full_ema_pre-trip.csv")
#str(emas_all)

emas_pre$rt <- as.numeric(emas_pre$rt)
emas_pre$response <- as.numeric(emas_pre$response)
emas_pre$ema_number <- emas_pre$session_number
#emas_pre$day_num <- ceiling(emas_pre$session_number / 3)


tibble(
  step = "only pre-trip data",
  n_trial_rows = nrow(emas_pre),
  n_sessions = nrow(emas_pre) / 24,
  n_pts = n_distinct(emas_pre$PUNS_ID)
) %>% gt() %>% tab_options(table.width = pct(80))
```



### fix valence var 
```{r}
table(emas_pre$valence)

#------------------------------------------------------------------------------#
# what i had in og code 
# emas_pre$delta_valence <- ifelse(emas_pre$valence == "PosPos" | emas_pre$trial_type == "NegNeg", 0,
#                      ifelse(emas_pre$right_valence == "positive", 1, -1))
# 

#------------------------------------------------------------------------------#



#table(emas_pre$valence)

# when value of emas_pre$valence col = negneg or pospos / emas_pre$delta_valence = 0
# when value of emas_pre$valence col = posneg...
  # emas_pre$delta_valence = -1 if right_valence = negative (POSITIVE WORD ON LEFT HAND SIDE)
  # / OR /
  # emas_pre$delta_valence = +1 if right_valence = positive (POSITIVE WORD ON RIGHT HAND SIDE)
#------------------------------------------------------------------------------#
emas_pre$delta_valence <- ifelse(emas_pre$valence %in% c("PosPos", "NegNeg"), 0,
                          ifelse(emas_pre$right_valence == "positive", 1, -1))
#------------------------------------------------------------------------------#
#trial type counts
table(emas_pre$delta_valence)



```




## Create var chose_pos
```{r}

# create chose_pos
  # delta_valence = +1 means positive word is on the right
  # delta_valence = -1 means positive word is on the left
  # response = 0 means they chose left, response = 1 means they chose right
  # sooo... when chose_pos = 1 pt picked the side the positive word was on


emas_pre$chose_pos  <- ifelse(emas_pre$delta_valence == 0, NA,
                        ifelse(emas_pre$delta_valence == 1,
                               ifelse(emas_pre$response == 1, 1, 0),
                               ifelse(emas_pre$response == 0, 1, 0)))
# num of posneg trials
sum(!is.na(emas_pre$chose_pos))


```

## Create delta_posneg_sb
```{r}
# Positive word's base rating minus negative word's base rating.
# valence = +1 is NEGPOS aka positive word is on the right: right_rating - left_rating
# valence = -1 is POSNEG aka positive word is on the left: left_rating - right_rating
# valence = 0 is POSPOS or NEGNEG 

emas_pre$delta_posneg_sb  <- ifelse(emas_pre$delta_valence == 0, NA,
                              ifelse(emas_pre$delta_valence == 1,
                                     emas_pre$right_base_rating - emas_pre$left_base_rating,
                                     emas_pre$left_base_rating - emas_pre$right_base_rating))


# within subj z score 

emas_pre <- emas_pre %>%
  group_by(PUNS_ID) %>%
  mutate(delta_posneg_sb_z_within = as.numeric(scale(delta_posneg_sb))) %>%
  ungroup()

# across subj z score 

emas_pre <- emas_pre %>%
  mutate(delta_posneg_sb_z = as.numeric(scale(delta_posneg_sb))) 

# across subj normed

emas_pre <- emas_pre %>% 
  mutate(delta_posneg_sb_normed = as.numeric(delta_posneg_sb / 200))


```

## Create delta_sb
```{r}
# Same thing as r_diff_norm in sandarsh's code (right rating - left rating)
emas_pre$delta_sb <- (emas_pre$right_base_rating - emas_pre$left_base_rating)

# within subj z score 
emas_pre <- emas_pre %>%
  group_by(PUNS_ID) %>%
  mutate(delta_sb_z_within = as.numeric(scale(delta_sb))) %>%
  ungroup()

# across subj z score 
emas_pre <- emas_pre %>%
  mutate(delta_sb_z = as.numeric(scale(delta_sb))) %>%
  ungroup()

# across subj normed
emas_pre <- emas_pre %>% 
  mutate(delta_sb_normed = as.numeric(delta_sb / 200))

# within subj normed
    # "Δself-belief was subject-
    # centered to remove between-subject differences in the use of the scale from the pre-task ratings. This
    # was done by first computing, on each trial, the difference between the participant’s self-belief ratings
    # for the right and left words. For each participant, these differences were then rescaled by subtracting
    # the participant-specific minimum difference and dividing by the participant-specific range (i.e., the
    # maximum minus the minimum), resulting in values bounded between 0 and 1."Finally, the rescaled
    # values were shifted by subtracting 0.5, yielding a centered measure ranging from −0.5 to 0.5."
emas_pre <- emas_pre %>%
  group_by(PUNS_ID) %>%
  # rescale delta_sb to be between 0 and 1 using this: (delta_sb - min) / (max - min) (this is standard min-max normalization formula)
  mutate(delta_sb_rescaled = (delta_sb - min(delta_sb, na.rm = TRUE)) / 
           (max(delta_sb, na.rm = TRUE) - min(delta_sb, na.rm = TRUE))) %>% 
  # center rescaled values on 0  with a range -0.5 to 0.5 by subtracting by 0.5
  mutate(delta_sb_within_subj_normed = delta_sb_rescaled - 0.5) %>%
  ungroup()
```


# Distibution of delta_posneg_sb and delta_sb 
```{r}
#emas_all %>%
#  mutate(delta_bin = cut(delta_posneg_sb, breaks = 20)) %>%
#  group_by(delta_bin) %>%
#  summarise(
#    n = n(),
#    n_timeout = sum(is.na(response) | is.na(rt)),
#    pct_timeout = round(n_timeout / n * 100, 1),
#    n_invalid = sum(valid_response == FALSE | is.na(valid_response)),
#    pct_invalid = round(n_invalid / n * 100, 1)
#  ) %>%
#  print(n = 20)



hist(emas_pre$delta_posneg_sb, breaks = 20)


hist(emas_pre$delta_sb, breaks = 20)


#----------------------------------------------------------------------------#
emas_pre$is_noresponse <- emas_pre$valid_response == FALSE | is.na(emas_pre$valid_response)

emas_pre$under_200ms <- emas_pre$rt < 200

emas_pre$somehow_over_5000ms <- emas_pre$rt > 5000




emas_pre$rt_quality <- case_when(
  emas_pre$is_noresponse ~ "no_response",
  emas_pre$under_200ms ~ "under_200ms",
  emas_pre$somehow_over_5000ms ~ "somehow_over_5000ms",
  TRUE ~ "valid"
)
emas_pre$rt_quality <- factor(emas_pre$rt_quality,
                               levels = c("valid", "no_response", "under_200ms", "somehow_over_5000ms"))


table(emas_pre$rt_quality)
#----------------------------------------------------------------------------#

# delta_posneg_sb
# p1 <- emas_all %>%
#   ggplot(aes(x = delta_posneg_sb, fill = rt_quality)) +
#   geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
#   scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
#                                 "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
#                     name = "trial quality") +
#   labs(title = "ALL DATA (delta_posneg_sb)", x = "delta_posneg_sb", y = "count") +
#   theme_minimal()



p2 <- emas_pre %>%
  ggplot(aes(x = delta_posneg_sb, fill = rt_quality)) +
  geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
  scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
                                "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
                    name = "trial quality") +
  labs(title = "PRE TRIP DATA (delta_posneg_sb)", x = "delta_posneg_sb", y = "count") +
  theme_minimal()

# p3 <- emas_post %>%
#   ggplot(aes(x = delta_posneg_sb, fill = rt_quality)) +
#   geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
#   scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
#                                 "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
#                     name = "trial quality") +
#   labs(title = "POST TRIP DATA (delta_posneg_sb)", x = "delta_posneg_sb", y = "count") +
#   theme_minimal()

# delta_sb
# p4 <- emas_all %>%
#   ggplot(aes(x = delta_sb, fill = rt_quality)) +
#   geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
#   scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
#                                 "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
#                     name = "trial quality") +
#   labs(title = "ALL DATA (delta_sb)", x = "delta_sb", y = "count") +
#   theme_minimal()

p5 <- emas_pre %>%
  ggplot(aes(x = delta_sb, fill = rt_quality)) +
  geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
  scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
                                "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
                    name = "trial quality") +
  labs(title = "PRE TRIP DATA (delta_sb)", x = "delta_sb", y = "count") +
  theme_minimal()

# p6 <- emas_post %>%
#   ggplot(aes(x = delta_sb, fill = rt_quality)) +
#   geom_histogram(bins = 30, position = "stack", color = "white", alpha = 0.85) +
#   scale_fill_manual(values = c("valid" = "blue", "no_response" = "red",
#                                 "under_200ms" = "orange", "somehow_over_5000ms" = "purple"),
#                     name = "trial quality") +
#   labs(title = "POST TRIP DATA (delta_sb)", x = "delta_sb", y = "count") +
#   theme_minimal()

#(p1 | p4) / (p2 | p5) / (p3 | p6) +
  #plot_annotation(title = "trial quality by delta_posneg_sb and delta_posneg")
(p2 | p5) +
  plot_annotation(title = "trial quality by delta_posneg_sb and delta_posneg")

#----------------------------------------------------------------------------#


#----------------------------------------------------------------------------#
# Tables


emas_pre %>%
  mutate(delta_posneg_sb_bin = cut(delta_posneg_sb, breaks = 20)) %>%
  group_by(delta_posneg_sb_bin) %>%
  summarise(
    n  = n(),
    n_no_response = sum(rt_quality == "no_response"),
    pct_no_response = round(n_no_response / n * 100, 1),
    n_under_200ms = sum(rt_quality == "under_200ms"),
    pct_under_200ms = round(n_under_200ms / n * 100, 1),
    n_somehow_over_5000ms = sum(rt_quality == "somehow_over_5000ms"),
    pct_somehow_over_5000ms  = round(n_somehow_over_5000ms / n * 100, 1)
  )



```

### Which affect_z binning is best? 
```{r}
colors_affect <- c(
  "unpleasant" = "#B2182B",
  "neutral"    = "#808080",
  "pleasant"   = "#2166AC"
)
compare_bins_wide <- bind_rows(

  # ±1.5 SD
  emas_pre %>%
    mutate(
      bins = "-1.5 SD, 0, 1.5 SD",
      affect_bin = case_when(
        affect_z <= -1.5 ~ "unpleasant",
        affect_z >=  1.5 ~ "pleasant",
        TRUE             ~ "neutral"
      )
    ),

  # ±1 SD
  emas_pre %>%
    mutate(
      bins = "-1 SD, 0, 1 SD",
      affect_bin = case_when(
        affect_z <= -1 ~ "unpleasant",
        affect_z >=  1 ~ "pleasant",
        TRUE           ~ "neutral"
      )
    ),

  # ±0.6 SD
  emas_pre %>%
    mutate(
      bins = "-0.6 SD, 0, 0.6 SD",
      affect_bin = case_when(
        affect_z <= -0.6 ~ "unpleasant",
        affect_z >=  0.6 ~ "pleasant",
        TRUE             ~ "neutral"
      )
    )
) %>%
  group_by(bins, affect_bin) %>%
  summarise(
    n = n(),
    mean_affect_z = mean(affect_z, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = affect_bin,
    values_from = c(n, mean_affect_z)
  ) %>%
  select(
    bins,
    n_unpleasant,
    n_neutral,
    n_pleasant,
    mean_affect_z_unpleasant,
    mean_affect_z_neutral,
    mean_affect_z_pleasant
  )



compare_bins_wide
#-----------------------------------------------------------------------------#
# Counts
plot_counts <- compare_bins_wide %>%
  select(bins, n_unpleasant, n_neutral, n_pleasant) %>%
  pivot_longer(
    cols = c(n_unpleasant, n_neutral, n_pleasant),
    names_to = "affect_bin",
    values_to = "count"
  ) %>%
  mutate(
    affect_bin = recode(
      affect_bin,
      n_unpleasant = "unpleasant",
      n_neutral = "neutral",
      n_pleasant = "pleasant"
    )
  )

#-----------------------------#
plot_counts$affect_bin <- factor(plot_counts$affect_bin, levels = c("unpleasant", "neutral", "pleasant"))

p_counts <- ggplot(plot_counts, aes(x = bins, y = count, fill = affect_bin)) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  scale_fill_manual(values = colors_affect) +
  labs(
    x = "affect_z bin possibility",
    y = "num trials",
    fill = "affect_z"
  ) +
  ggtitle("num trials") +
  theme_classic()


#-----------------------------------------------------------------------------#
# Mean
plot_box <- bind_rows(

  emas_pre %>%
    mutate(
      bins = "-1.5 SD, 0, 1.5 SD",
      affect_bin = case_when(
        affect_z <= -1.5 ~ "unpleasant",
        affect_z >=  1.5 ~ "pleasant",
        TRUE             ~ "neutral"
      )
    ),

  emas_pre %>%
    mutate(
      bins = "-1 SD, 0, 1 SD",
      affect_bin = case_when(
        affect_z <= -1 ~ "unpleasant",
        affect_z >=  1 ~ "pleasant",
        TRUE           ~ "neutral"
      )
    ),

  emas_pre %>%
    mutate(
      bins = "-0.6 SD, 0, 0.6 SD",
      affect_bin = case_when(
        affect_z <= -0.6 ~ "unpleasant",
        affect_z >=  0.6 ~ "pleasant",
        TRUE             ~ "neutral"
      )
    )
) %>%
  mutate(
    affect_bin = factor(
      affect_bin,
      levels = c("unpleasant", "neutral", "pleasant")
    )
  )
#-----------------------------#
p_box <- ggplot(
  plot_box,
  aes(x = bins,
      y = affect_z,
      fill = affect_bin)
) +
  geom_boxplot(
    position = position_dodge(width = 0.8),
    width = 0.7,
    outlier.alpha = 0.2
  ) +
  scale_fill_manual(values = colors_affect) +
  labs(
    x = "affect_z bin possibility",
    y = "mean affect_z",
    fill = "affect_z"
  ) +
  ggtitle("distribution of affect_z means by binning possibility") +
  theme_classic()

#-----------------------------#
p_counts + p_box
```



## Create affect_z_bin
```{r}
# Thirds ( affect_z < 0.5 /  affect_z_bin = unpleasant
#         mid third of affect_z /  affect_z_bin = neutral
#         lower third of affect_z affect_z > 0.5  /  affect_z_bin = pleasant)


# pre
emas_pre$affect_z_bin <- ifelse(emas_pre$affect_z < -0.6, "unpleasant",
                           ifelse(emas_pre$affect_z > 0.6, "pleasant", "neutral"))
emas_pre$affect_z_bin <- factor(emas_pre$affect_z_bin,
                                  levels = c("unpleasant", "neutral", "pleasant"))




# Counts 

# affect_z_bin counts (pre)
cat("---pre data---")
nrow(emas_pre)
table(emas_pre$affect_z_bin)

```


## Create delta_posneg_sb_z_bin
```{r}
#-----ranges-------------------------------------------------------------------
range(emas_pre$delta_posneg_sb_z, na.rm = TRUE)
#seq(-2.374684, 1.447656)
range(emas_pre$delta_posneg_sb_z_within, na.rm = TRUE)
#seq(-2.72815, 1.795692)
range(emas_pre$delta_posneg_sb, na.rm = TRUE)
#seq(-100  100)
range(emas_pre$delta_posneg_sb_normed, na.rm = TRUE)
# (-0.5 to 0.5)
#-------bins across person z score--------------------------------------------
# pre
emas_pre$delta_posneg_sb_z_bin <- cut(emas_pre$delta_posneg_sb_z, 
                                        # breaks = seq(-3.15, 1.80, length.out = 12), # 11 bins
                                         breaks = seq(-2.5, 1.5, length.out = 6), # 5 bins # AS OF 07.08 figure out a way next time to do this so i dont have to manually plug in min and max 
                                         include.lowest = TRUE)
#-------bins within person z score---------------------------------------------
# pre
emas_pre$delta_posneg_sb_z_within_bin <- cut(emas_pre$delta_posneg_sb_z_within, 
                                         breaks = seq(-2.8, 1.8, length.out = 6), # 5 bins
                                         include.lowest = TRUE)
#-------bins og scale ---------------------------------------------

# pre
emas_pre$delta_posneg_sb_bin <- cut(emas_pre$delta_posneg_sb, 
                                         breaks = seq(-100, 100, length.out = 6),# 5 bins
                                         labels = c("-100 to -60", "-60 to -20", "-20 to 20", "20 to 60", "60 to 100"),
                                         include.lowest = TRUE)
# as factor

emas_pre$delta_posneg_sb_bin <- factor(emas_pre$delta_posneg_sb_bin,
                                   levels = c("-100 to -60", "-60 to -20", "-20 to 20", "20 to 60", "60 to 100"))


#-------bins normed (/200) ---------------------------------------------

# pre
emas_pre$delta_posneg_sb_normed_bin <- cut(emas_pre$delta_posneg_sb_normed, 
                      breaks = seq(-0.5, 0.5, length.out = 6),
                      labels = c("-0.5 to -0.3",  
                                 "-0.3 to -0.1", "-0.1 to 0.1", "0.1 to 0.3", "0.3 to 0.5"),
                      include.lowest = TRUE)
# as factor
emas_pre$delta_posneg_sb_normed_bin <- factor(emas_pre$delta_posneg_sb_normed_bin,
                                   levels = c("-0.5 to -0.3",  "-0.3 to -0.1", "-0.1 to 0.1", "0.1 to 0.3", "0.3 to 0.5"))

# Counts 
cat("\n--------delta_posneg_sb_z_bin counts--------\n")
cat("\n--------------------------------------------\n")
# delta_posneg_sb_z_bin counts (all)

cat("\n---pre data---\n")
# delta_posneg_sb_z_bin counts (pre)
table(emas_pre$delta_posneg_sb_z_bin)

cat("\n \n")


cat("\n----delta_posneg_sb_z_within_bin counts----\n")
cat("\n--------------------------------------------\n")

cat("\n---pre data---\n")
table(emas_pre$delta_posneg_sb_z_within_bin)

cat("\n \n")


cat("\n----------delta_posneg_sb_bin counts--------\n")
cat("\n--------------------------------------------\n")

cat("\n---pre data---\n")
table(emas_pre$delta_posneg_sb_bin)

cat("\n \n")

cat("\n----------delta_posneg_sb_normed_bin counts--------\n")

cat("\n---pre data---\n")
table(emas_pre$delta_posneg_sb_normed_bin)

cat("\n \n")

```
## Create delta_sb_z_bin
```{r}
#-----ranges-------------------------------------------------------------------
range(emas_pre$delta_sb_z, na.rm = TRUE)
#(-2, 2)
#(-2.5, 2.5)


range(emas_pre$delta_sb_z_within, na.rm = TRUE)
#seq(-2.5, 2.5)

range(emas_pre$delta_sb, na.rm = TRUE)
#(-97, 100)

range(emas_pre$delta_sb_normed, na.rm = TRUE)
#(-0.5, 0.5)

range(emas_pre$delta_sb_within_subj_normed, na.rm = TRUE)

#-------bins across person z score--------------------------------------------

# pre
emas_pre$delta_sb_z_bin <- cut(emas_pre$delta_sb_z, 
                                        # breaks = seq(-3.15, 1.80, length.out = 12), # 11 bins
                                         breaks = seq(-2, 2, length.out = 6), # 5 bins
                                         include.lowest = TRUE)



#-------bins within person z score---------------------------------------------


# pre
emas_pre$delta_sb_z_within_bin <- cut(emas_pre$delta_sb_z_within, 
                                         breaks = seq(-2.5, 2.5, length.out = 6), # 5 bins
                                         include.lowest = TRUE)




#-------bins og scale ---------------------------------------------


# pre
emas_pre$delta_sb_bin <- cut(emas_pre$delta_sb, 
                                         breaks = seq(-100, 100, length.out = 6), # 5 bins
                                         labels = c("-100 to -60", "-60 to -20", "-20 to 20", "20 to 60", "60 to 100"),
                                         include.lowest = TRUE)


# as factor

emas_pre$delta_sb_bin <- factor(emas_pre$delta_sb_bin,
                                   levels = c("-100 to -60", "-60 to -20", "-20 to 20", "20 to 60", "60 to 100"))



#-------bins normed (/200) ---------------------------------------------



# pre
emas_pre$delta_sb_normed_bin <- cut(emas_pre$delta_sb_normed, 
                      breaks = seq(-0.5, 0.5, length.out = 6),
                      labels = c("-0.5 to -0.3",  
                                 "-0.3 to -0.1", "-0.1 to 0.1", "0.1 to 0.3", "0.3 to 0.5"),
                      include.lowest = TRUE)





#-------bins within sjuject normed normed FOR PLOTS ---------------------------------------------


# pre
emas_pre$delta_sb_within_subj_normed_bin <- cut(emas_pre$delta_sb_within_subj_normed, 
              breaks = seq(-0.5, 0.5, length.out = 6),
              labels = c("-0.5 to -0.3", "-0.3 to -0.1", "-0.1 to 0.1", "0.1 to 0.3", "0.3 to 0.5"),
              include.lowest = TRUE)



# as factor

emas_pre$delta_sb_within_subj_normed_bin <- factor(emas_pre$delta_sb_within_subj_normed_bin,
                                   levels = c("-0.5 to -0.3", "-0.3 to -0.1", "-0.1 to 0.1", "0.1 to 0.3", "0.3 to 0.5"))


# Counts 
cat("\n--------delta_sb_z_bin counts--------\n")
# delta_posneg_sb_z_bin counts (all)
cat("\n---pre data---\n")
# delta_posneg_sb_z_bin counts (pre)
table(emas_pre$delta_sb_z_bin)
cat("\n \n")


cat("\n----delta_sb_z_within_bin counts----\n")
cat("\n---pre data---\n")
table(emas_pre$delta_sb_z_within_bin)
cat("\n \n")



cat("\n----------delta_sb_bin counts--------\n")
cat("\n---pre data---\n")
table(emas_pre$delta_sb_bin)
cat("\n \n")


cat("\n----------delta_sb_normed_bin counts--------\n")
cat("\n---pre data---\n")
table(emas_pre$delta_sb_normed_bin)
cat("\n \n")




cat("\n----------delta_sb_within_subj_normed_bin counts--------\n")
cat("\n---pre data---\n")
table(emas_pre$delta_sb_within_subj_normed_bin)
cat("\n \n")

```


## Create p_chose_pos_by_ema (by pt by ema) ONLY OUT OF POSNEG TRIALS
```{r}

# pre
emas_pre <- emas_pre %>% group_by(PUNS_ID, ema_number) %>%
  mutate(p_chose_pos_by_ema = mean(chose_pos, na.rm = TRUE)) %>%
  ungroup()

colnames(emas_pre)
```

## Create p_chose_pos_by_affect_z_bin (by pt by ema) ONLY OUT OF POSNEG TRIALS
```{r}
# pre
emas_pre <- emas_pre %>%
  group_by(PUNS_ID, affect_z_bin) %>%
  mutate(p_chose_pos_by_affect_z_bin = mean(chose_pos, na.rm = TRUE)) %>%
  ungroup()

```


## QC
```{r}
# before
table(emas_pre$rt_quality) 

# clean
emas_pre  <- emas_pre  %>% filter(rt_quality == "valid", !is.na(response), !is.na(rt))

# after

cat("\n-------------\n")
nrow(emas_pre)
n_distinct(emas_pre$PUNS_ID)



#colSums(is.na(emas_pre))
```


## Another Clean for RTs and other NAs and make posneg df
```{r}
#-----------------------------------------------------------------------#
nrow(emas_pre)
n_distinct(emas_pre$PUNS_ID)
list(unique(emas_pre$PUNS_ID))

emas_pre <- emas_pre %>%
         filter(!is.na(affect_z),
         !is.na(rt),
         rt >= 200,
         rt <= 5000)
nrow(emas_pre)
n_distinct(emas_pre$PUNS_ID)
list(unique(emas_pre$PUNS_ID))


#-----------------------------------------------------------------------#

posneg_pre <- emas_pre %>%
  filter(!is.na(chose_pos))

nrow(posneg_pre)

n_distinct(posneg_pre$PUNS_ID)
list(unique(posneg_pre$PUNS_ID))

table(posneg_pre$valence)
table(posneg_pre$delta_valence)

```




# Pre-Trip Compliance
```{r}
pt_compliance <- emas_pre %>%
  group_by(PUNS_ID) %>%
  summarise(
    n_emas = n_distinct(ema_number),
    compliance = n_emas / 30
  ) %>%
  ungroup() %>%
  arrange(desc(compliance))

pt_compliance %>%
  gt() %>%
  fmt_percent(columns = compliance, decimals = 1) %>%
  tab_header(title = "Pre-trip EMA compliance by participant") %>%
  tab_options(table.width = pct(80))

# summary row
tibble(
  n_pts = length(pt_compliance$compliance),
  mean_compliance = mean(pt_compliance$compliance),
  median_compliance = median(pt_compliance$compliance),
  min_compliance = min(pt_compliance$compliance),
  max_compliance = max(pt_compliance$compliance)
) %>%
  gt() %>%
  fmt_percent(columns = mean_compliance:max_compliance, decimals = 1) %>%
  tab_header(title = "Overall compliance (PRE TRIP ONLY)") %>%
  tab_options(table.width = pct(80))



```



# MODEL: PREDICTED chose_pos ~ delta_posneg_sb by affect_z WITH EFFECT OF TIME (pretrip)
```{r}
# Choice
  # Attempt 1: boundary (singular) fit: see help('isSingular')
    # choice_model_pretrip <- glmer(chose_pos ~ affect_z + delta_posneg_sb + ema_number +
    #                            (1 + affect_z + delta_posneg_sb + ema_number | PUNS_ID),
    #                          data = posneg_pre, family = binomial)

  # Attempt 2: converged and in hypothesized direction. sigificant positive main effect     of affect_z was positive aka in means pts are more likely to describe themselves          with the positive word in a pair when they are in a more pleasant mood than usual.       and when in more unpleasant mood than usual they are more likely to describe            themselves with the negative word in a pair 
 
choice_model_pretrip <- glmer(chose_pos ~ affect_z + delta_posneg_sb + ema_number +
                                (1 + affect_z + delta_posneg_sb + ema_number || PUNS_ID),
                              data = posneg_pre, family = binomial)

#v3plot_1b_model
summary(choice_model_pretrip)

```


# MODEL: PREDICTED rt_z ~ delta_posneg_sb by affect_z WITH EFFECT OF TIME (pretrip)
```{r}
# RT
# z score within pt
posneg_pre <- posneg_pre %>%
  group_by(PUNS_ID) %>%
  mutate(rt_s = rt / 1000) %>%
  mutate(rt_z = as.numeric(scale(rt_s))) %>%
  ungroup()

# create orthogonal  terms (setting degree to 2 create a lin and quadratic term )
poly_matrix_rt <- poly(posneg_pre$delta_posneg_sb, degree = 2)
posneg_pre$delta_posneg_sb_lin  <- poly_matrix_rt[, 1]
posneg_pre$delta_posneg_sb_quad <- poly_matrix_rt[, 2]


  # Attempt 1: Warning :Model failed to converge with 3 negative eigenvalues: -1.6e-01 -2.8e-01 -4.4e-01 and
              # boundary (singular) fit: see help('isSingular')
    # rt_model_pretrip <- lmerTest::lmer(
    #   rt_z ~ affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number +
    #     (1 + affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number | PUNS_ID),
    #   data = posneg_pre
    # )
  
  # Attempt 2: Warning :Model failed to converge with max|grad| = 0.420296 (tol = 0.002, component 1) and
              # Warning :Model is nearly unidentifiable: very large eigenvalue 
                  # - Rescale variables?;Model is nearly unidentifiable: large eigenvalue ratio
                  # - Rescale variables?
    # rt_model_pretrip <- lmerTest::lmer(
    #   rt_z ~ affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number +
    #     (1 + affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number || PUNS_ID),
    #   data = posneg_pre
    # )

  # Attempt 3: Warning :Model failed to converge with max|grad| = 0.364055 (tol = 0.002, component 1) and
              # Warning :Model is nearly unidentifiable: very large eigenvalue 
                  # - Rescale variables?;Model is nearly unidentifiable: large eigenvalue ratio
                  # - Rescale variables?
    # rt_model_pretrip <- lmerTest::lmer(
    #   rt_z ~ affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number +
    #     (1 + affect_z + delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number || PUNS_ID),
    #   data = posneg_pre)
  
  # Attempt 4: 
      rt_model_pretrip <- lmerTest::lmer(
        rt_z ~ affect_z * delta_posneg_sb_lin + delta_posneg_sb_quad + ema_number +
          (1 + affect_z + delta_posneg_sb_lin + delta_posneg_sb_quad || PUNS_ID),
        data = posneg_pre)
summary(rt_model_pretrip)

```



# PREDICTED CHOICE AND RT MODEL TABLES
```{r}
#-------------------------------------------------------------------------------#
# CHOICE
choice_model_pretrip_tbl <- tbl_regression(choice_model_pretrip)

choice_model_pretrip_tbl_pretty <-
  tbl_merge(
    tbls = list(choice_model_pretrip_tbl),
    tab_spanner = c("**Pre-trip Data only**")
  )
#choice_model_pretrip_tbl_pretty

#-------------------------------------------------------------------------------#
# RT

rt_model_pretrip_tbl <- tbl_regression(rt_model_pretrip)

rt_model_pretrip_tbl_pretty <-
  tbl_merge(
    tbls = list(rt_model_pretrip_tbl),
    tab_spanner = c("**Pre-trip Data only**")
  )
#rt_model_pretrip_tbl_pretty



#-------------------------------------------------------------------------------#
# combined
combined_model_tbl <- tbl_merge(
  tbls = list(choice_model_pretrip_tbl, rt_model_pretrip_tbl),
  tab_spanner = c("**Predicted Choice**", "**Predicted RT (ms)**")
)

# Print the table
combined_model_tbl
```




# PROCESSED DF 
```{r}

# define folder
processed_folder <- "processed_data"

# make it if dont exist
if (!dir.exists(processed_folder)) dir.create(processed_folder)

# build filename
filename_processed <- ("processed_empirical_data_posneg.csv")
filename_processed_full <- paste0("processed_empirical_data_full.csv")

# export
write_csv(posneg_pre, file.path(processed_folder, filename_processed))

write_csv(emas_pre, file.path(processed_folder, filename_processed_full))

```



# EXPORT CSVS FOR MODELING (WITH ALL TRIAL TYPES) AT THIS POINT
```{r}
# mass comment/uncomment: command + shift + C



# prep for hssm
# emas_pre <- emas_pre %>%
#   mutate(
#     response = if_else(response == 0, -1, response),
#     rt = as.numeric(rt),
#     PUNS_ID = as.character(PUNS_ID)
#   ) %>%
#   rename(subject = PUNS_ID)

emas_pre <- emas_pre %>%
  mutate(
    response = if_else(response == 0 | response == -1, -1, 1),
    rt = as.numeric(rt),
    PUNS_ID = as.character(PUNS_ID)
  ) %>%
  rename(subject = PUNS_ID)

table(emas_pre$response)
#-----------------------------------------------------------------------------#

# define folder
folder <- "hssm_ema_dfs_for_cluster"

# make it if dont exist

if (!dir.exists(folder)) dir.create(folder)

# build filname
filename_pre <- "hssm_ema_df_pre.csv"

# export
write_csv(emas_pre, file.path(folder, filename_pre))
#str(emas_pre)
```


